---
title: 
output: 
  word_document:
    reference_docx: styles_ref.docx
---

```{r, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(leaflet)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))

knitr::opts_chunk$set(warning=FALSE)

library(knitr)
library(markdown)
library(rmarkdown)
```

```{r, include=FALSE}

dbns <- cte_data2[rownames(cte_data2)==dbn,]
school_name <- dbns$Location.Name
open_date <- dbns$Open.Date
address <- dbns$Primary.Address
city <- dbns$City
nta <- dbns$NTA_Name
district <- dbns$Geographical.District.Code

principal_name <- dbns$Principal.Name
principal_title <- dbns$Principal.Title
principal_contact <- dbns$Principal.Phone.Number

bfsc_dir_name <- dbns$BFSC.Director.Name
bfsc_dir_title <- dbns$BFSC.Director.Title
bfsc_dir_phone <- dbns$BFSC.Director.Phone

grades <- dbns$Grades.Final

grad_rate_4yr <- dbns$Metric.Value...Graduation.Rate..4.year * 100.00
grad_rate_6yr <- dbns$Metric.Value...Graduation.Rate..6.Year * 100.00

cri_4yr <- dbns$Metric.Value...Four.Year.College.Readiness.Index * 100.00
cri_6yr <- dbns$Metric.Value...College.Readiness.Index..6.Year * 100.00

enrollment_1516 <- dbns$X2015.16
enrollment_1617 <- dbns$X2016.17

cte_enr_1516 <- dbns$X2015_16_CTE_Enr
cte_enr_1617 <- dbns$X2016_17_CTE_Enr

perc_cte_enr_1516 <- round((cte_enr_1516 / enrollment_1516),2) * 100.00
perc_cte_enr_1617 <- round((cte_enr_1617 / enrollment_1617),2) * 100.00

cte_credits_1516 <- dbns$CTE_credits_201516
cte_credits_1617 <- dbns$CTE_credits_201617


enr_trend <- dbns %>%
                select(X2012.13, X2013.14, X2014.15, X2015.16, X2016.17)


enr_trend_melt <- melt(enr_trend) %>%
                    rename(c("variable"  = "Year")) %>%
                    rename(c("value" = "enrollment"))


enr_trend_melt$Year <-gsub('X','',enr_trend_melt$Year)

enr_trend_melt



enr_graph <- ggplot(data=enr_trend_melt, aes(x=Year, y=enrollment, group=1)) + 
                  geom_line(colour = "blue") +
                  geom_point(colour="green", size=3, shape=21, fill="white") + 
                  theme(axis.text.x=element_text(angle=60, hjust=1)) + ggtitle("Enrollment Trend") + 
                  theme(plot.title = element_text(colour="brown", size=10))

```
# `r school_name`
DBN: `r dbn`

Open Date: `r open_date`

data as of `r Sys.Date()`

<br>

## Location and Contacts

### Location
  
`r address`, `r city`, `r nta`, District `r district`
    

<br>
     
### Principal

`r principal_title`: `r principal_name` 
    
Contact: `r principal_contact` 

<br>
    
### Borough Field Support Center

`r bfsc_dir_title`: `r bfsc_dir_name` 
    
Contact: `r bfsc_dir_phone` 

<br>
    
### Grades 
`r grades`
    
<br>

## Stats

### 2015-16 Graduation and College Readiness

4-Year Graduation Rate: `r grad_rate_4yr`%

6-Year Graduation Rate: `r grad_rate_6yr`%


4-Year College Readiness Index: `r cri_4yr`%

6-Year College Readiness Index: `r cri_6yr`%

<br> 

### Enrollment: 

* 2015-16: `r enrollment_1516` students

* 2016-17: `r enrollment_1617` students

<br> 

```{r, fig.width=2.5, fig.height=2.5, echo=FALSE}

enr_graph

```


##### Page Break 

CTE Enrolled

* 2015-16: `r cte_enr_1516`, `r perc_cte_enr_1516`% of total enrollment

* 2016-17: `r cte_enr_1617`, `r perc_cte_enr_1617`% of total enrollment

<br> 

CTE Credits 

* 2015-16: `r format(cte_credits_1516, digits=2, nsmall=2, big.mark=",")` credits

* 2016-17: `r format(cte_credits_1617, digits=2, nsmall=2, big.mark=",")` credits


<br>


## CTE Programs

<br>

These are the 2016-17 funded CTE Programs: 

<br> 

```{r, include=FALSE}

cte_pgms <- read.csv("D:/cte_one_pager/pgms_funded.csv") %>%
              filter(DBN == dbn) %>%
              select(Program.Name, Program.CIP.Code)
              
```


```{r, echo=FALSE}

kable(cte_pgms)

```

<br>

## School Program Inventory

<br> 

This school program inventory list is as of May 2017. 

<br> 

```{r, include=FALSE}

other_pgms <- read.csv("D:/cte_one_pager/opsr_ml.csv") %>%
              filter(DBN == dbn) %>%
              select(School.Year, Program.Name)
              
```


```{r, echo=FALSE}

kable(other_pgms)

```

```{r, include=FALSE}

ps_teacher_sal <- dbns$Per.Student.Spending.on.Classroom.Teacher.Salaries
ps_pd <- dbns$Per.Student.Spending.on.Professional.Development
ps_summafschool <- dbns$Per.Student.Spending.on.Summer.and.After.School.Programs
t_total <- dbns$Total.Dollars.Spent.at.this.School
t_ps_cost <- dbns$Total.Per.Student.Cost.in.this.School
t_ps_gen_ed <- dbns$Total.Per.Student.Spending.for.General.Ed.Students
t_ps_spec_ed <- dbns$Total.Per.Student.Spending.for.Special.Ed.Students

cost_entire_system <- read.csv("D:/cte_one_pager/cost_entire_system.csv")

es_ps_teacher_sal <- cost_entire_system$Per.Student.Spending.on.Classroom.Teacher.Salaries
es_ps_pd <- cost_entire_system$Per.Student.Spending.on.Professional.Development
es_ps_summafschool <- cost_entire_system$Per.Student.Spending.on.Summer.and.After.School.Programs
es_t_total <- cost_entire_system$Total.Per.Student.Cost.For.Entire.System
es_t_ps_gen_ed <- cost_entire_system$Total.Per.Student.Spending.for.General.Ed.Students
es_t_ps_spec_ed <- cost_entire_system$Total.Per.Student.Spending.for.Special.Ed.Students




fsf_fy16 <- dbns$FY16.Projected.Formula
fsf_fy17 <- dbns$FY17.Projected.Formula
fsf_fy18 <- dbns$FY18.Projected.Formula

cte_fsf <- read.csv("D:/cte_one_pager/portfolio_cte_combined.csv", stringsAsFactors = FALSE) %>%
              filter(DBN == dbn)  %>%
              filter(Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula == "Tier 1 Programs" | 
                    Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula == "Tier 2 Programs"  | 
                    Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula == "Tier 3 Programs" | 
                    Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula == "Tier 4 Programs") %>%
              select(Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula, FY18Projected_Formula_3, DBN) 

names(cte_fsf)

cte_fsf_amt_fy18 <- sum(cte_fsf$FY18Projected_Formula_3)


cte_fsf$Fair.Student.Funding.Formula.Details1.Fair.Student.Funding.Weighted.Register.Formula.Fair.Student.Funding.Weighted.Register.Formula

```


##### Page Break

## Funding


| 2015-16 Category                                          | `r dbn`            |Entire System         |  
|---------------------------------------------------------  |:------------------:|:--------------------:|
| Per Student Spending on Classroom Teacher Salaries        | `r ps_teacher_sal` |`r es_ps_teacher_sal` |
| Per Student Spending on Professional Development          | `r ps_pd`          |`r es_ps_pd`          |
| Per Student Spending on Summer and After School Programs  | `r ps_summafschool`|`r es_ps_summafschool`|
| Total Dollars Spent at this School                        | `r t_total`        | NA                   |
| Total Per Student Cost in this School                     | `r t_ps_cost`      |`r es_t_total`        |
| Total Per Student Spending for Special Ed Students        | `r t_ps_spec_ed`   |`r es_t_ps_spec_ed`   |
| Total Per Student Spending for General Ed Students        | `r t_ps_gen_ed`    |`r es_t_ps_gen_ed`    |

<br> 

## Fair Student Funding

<br>

FY18 Projected CTE Amount: $`r format(cte_fsf_amt_fy18, digits=0, nsmall=2, big.mark=",")`

<br>

This table shows the total FSF amount. 

<br> 

| Category/Year                                             |      Amount   |  
|---------------------------------------------------------  |:-------------:|
| FY16 Projected-Formula                                    | `r fsf_fy16`  |
| FY17 Projected-Formula                                    | `r fsf_fy17`  |
| FY18 Projected-Formula                                    | `r fsf_fy18`  |





